---
title: Metabolic differentiation facilitates coexistence in two coral reef fish species
author: "Simon J Brandl"
date: "05/04/2020"
output:
  md_document:
    variant: markdown_github
    toc: true
    toc_depth: 1
---

This repository contains the code and data to reproduce all tables and figures presented in Brandl et al. "Metabolic differentiation facilitates coexistence in two coral reef fish species." 

## Instructions
All analyses for the current project were done in R, using the drake pipeline as provided by the [drake](https://github.com/ropensci/drake) package. You can use the pipeline to compile all models, figures, and tables.
You can install `drake` from CRAN: 
```{r, eval=FALSE}
install.packages("drake")
```
Next you need to open an R session with working directory set to the root of the project.    

We use a number of packages, listed in `r/packages.R`. If needed, missing packages should first be installed. 

Then, to generate all figures, analyses, and tables, simply run:

```{r, eval = FALSE}
drake::r_make()
```

All output will be automatically rendered inside the folder called output. 

## Details
The elements of this project include: 

1) data: this folder includes all the raw data necessary to run the script.
2) output: this folder includesall outputs from the R-script.
3) documents: this folder includes the manuscript, appendices, and cover letter.
4) r: this folder contains three .R files, `packages.R`, `functions.R`, and `plan.R`.     
`packages.R` contains all packages needed, `functions.R` contains all functions to reproduce the analyses, and `plan.R` provides the code that binds each step of the workflow.

## Datasets

1. commdat = Community data: data were collected using enclosed clove-oil stations in both the lagoon and on the forereef around the island of Mo'orea, French Polynesia. Contains each caught individual of cryptobenthic fish (as rows), including the two target species. Columns specify each individuals corresponding sampling information (location, site, outcrop, lat & long, curved surface length, depth), identity, size, etc. All collections done in 2017, 2018, 2019, and 2020.

2. respodat = Respirometry: these data are derived from intermittent respirometry, performed in the lab at CRIOBE. Each row is an individual fish and its associated metadata. SMR = standard metabolic rate in mg O2 per h. MaxMR = maximum metabolic rate in mg O2 per h. MeanTemp...C. = temperature in ºCelsius. Weight..kg. = mass in g.

3. morpho = External morphology; gut.morpho = internal morphology: data derived from measurements performed on individuals collected from the field. Two different datasets for external and internal morphology. Each row is a unique individual with associated metadata and measurements for SL (mm), TL (mm), weight (g), girth (mm), vertical gape size (V_gape, mm), and horizontal gape size (H_gape, mm). Gut morpho is a smaller set but same setup, with the length of the gastrointestinal tract (GIT) in mm.

4. DNA gut content metabarcoding, three distinct datasets:
     a) gobies.meta = Metadata:      
     contains information on all sampled and processed individuals, with each individual havign a unique ID and its own row. IDs are critical to match with the two other datasets. 
     b) gobies.coi = COI primer data:    
     each row is an exact sequence variant (ESV) that was assigned to a prey taxon. Since this was part of a greater collection effort, there are many rows that are 0 across all columns. Columns 1:10 contain infromation about the sequence, while the remaining columns (G01 - G40) are individual fishes linked to the Extraction ID in the metadata. Values in the dataset are sequence abundances.
     c) goby.23s = 23S primer data:    
     Similar as gobie.coi

          
5. aquarium.trials = Feeding trials: data are observations from videos of sand gobies in varying configurations in aquaria. id = identity of the observed individual; species = species affiliation (F. neophytus or G. cauerensis); video =  video ID; treatment = configuration tested; feed = number of bites taken over the duration of the observations (30 minutes); before_after = before or after generic food addition -- only before data are used for this paper. All videos, labelled by their respective trial, are accessible under the following link: https://www.youtube.com/playlist?list=PL9LfYSgK5itOtyll0jJr7Kszdf6olw6Ce 

## Supplemental info
This paper was produced using the following software and associated packages:

```{r, echo=FALSE}
devtools::session_info()
```


All code written by Simon J. Brandl (simonjbrandl@gmail.com and https://github.com/simonjbrandl). Please contact me for any issue or question. 


